After subjects complete either experiment 1 or experiment 2, they
participate in a final experiment intended to test ability to
distinguish deepfake videos. At the outset of the experiment, subjects
are shown the following prompt:

\begin{quotation}
\emph{We're going show you a series of short videos involving current Democratic candidates for US President.}

\emph{As you may be aware, the technology for manipulating videos has been developing quickly, and it can sometimes be difficult to tell the difference between authentic videos and convincing-looking fakes. We'd like you to tell us which of the following videos you think have been manipulated.}

\emph{The videos that you'll be shown are randomly drawn from a larger pool, so it might be the case that some, all, or none of the videos have been manipulated. After you watch the videos, we will tell you which ones had been manipulated.}
\end{quotation}  

Here, we draw from publicly released deepfakes. For example:

\begin{itemize}
  \item \href{https://www.youtube.com/watch?v=cQ54GDm1eL0}{Original Buzzfeed video}
  \item \href{https://www.youtube.com/watch?v=s34NWArsxVw}{White House correspondents dinner} 
  \item \href{https://youtu.be/rvF5IA7HNKc?t=15}{Trump/Obama conversation Fallon}
  \item \href{https://www.youtube.com/watch?v=8PowkVIQI0E}{Coding Elite demo of Trump speech}
  \item \href{https://www.youtube.com/watch?v=J2yNZ0s9snU}{Trump interviews self in mirror}
  \item \href{https://www.youtube.com/watch?v=f0lFtwlG4N4}{Larry David / Bernie}
  \item \href{https://www.youtube.com/watch?v=Pe0nEej6l28}{Bernie getting shredded}
  \item \href{https://www.youtube.com/watch?v=RWZmLKw7PG8}{Hillary/Kate McKinnon crying on SNL}
  \item \href{https://youtu.be/nIU_DvjICnY?t=18}{Obama / Trevor Noah sex talk}
\end{itemize}

For each video, subjects are given a forced choice of deepfake/not deepfake.
